### 2023-01-05 ms.rmd
New rendered MS

   p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
  ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
```

@@

p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
        axis.text = element_text(size = 15))
   p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')

   ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
  ggsave(p2.2, filename = "./output/figures/fig2.2.png")
```

```{r, fig3, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)

>>>>

  p1.2
   p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')

   p1.2.2
  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
  ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
```

@@

p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
        axis.text = element_text(size = 15))
   p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
  p2
  p2.2
   ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
  ggsave(p2.2, filename = "./output/figures/fig2.2.png")
```

```{r, fig3, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
